Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Emphasize /code documentation/ on first usage
Shorten "Problem" -> "Hspec"

Hspec is thus useful for code documentation but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}.  It is integrated with with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence into a spec.
Code examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

The \texttt{describe} function combines a list of specs into a larger spec.
It can be used to organize a spec as a tree.
Internally, a \texttt{Writer} is used to build up specs in a monadic way.

A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested.  Behavior with evidence that does not
hold is reported to the developer.

%%%%%%%%%%%%%%%%
\subsubsection{Hspec does not provide a mechanism for expectations}
BDD frameworks use \emph{should} or \emph{must} instead of
\emph{assert} to express expectations.  Here is an example that uses
RSpec.

@@

%%%%%%%%%%%%%%%%
\subsubsection{Hspec provides no mechanism to expect exceptions}
RSpec provides a mechanism to expect exceptions.

>>>>

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}.  It is integrated with with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

@@

\noindent The {\tt it} function combines a text description for a
behavior and some evidence (a code example or a property) into a spec.
Code examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

The \texttt{describe} function combines a list of specs into a larger spec.
% It can be used to organize a spec as a tree.
% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested.  Behavior with evidence that does not
hold is reported to the developer.

%%%%%%%%%%%%%%%%
% \subsubsection{Hspec does not provide a mechanism for expectations}
BDD frameworks use \emph{should} or \emph{must} instead of
\emph{assert} to express expectations.  Here is an example that uses
RSpec.

@@

%%%%%%%%%%%%%%%%
% \subsubsection{Hspec provides no mechanism to expect exceptions}
Moreover RSpec provides a mechanism to expect exceptions.
